Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-06-03 noise_covid_v2.Rmd
incorporate info about LRT scan below figure

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, 
                      fig.align = "center", fig.width = 5,
                      fig.height = 5)
```

@@

{![Figure 2A. (1) Simulated p-values for the Wald test](./figures/pvals_sim_Wald.pdf){width=33%}![(2) Simulated p-values for the Likelihood-Ratio test](./figures/pvals_sim_LRT.pdf){width=33%}!
}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.align = "center", fig.width = 5,
                      fig.height = 5)
```

@@

![Figure 2A. (1) Simulated p-values for the Wald test](./figures/pvals_sim_Wald.pdf)
![(2) Simulated p-values for the Likelihood-Ratio test](./figures/pvals_sim_LRT.pdf)

@@

In some time windows, the Likelihood-Ratio statistic can't be computed because (TODO**: the weight matrix in the IRLS can't be calculated?).

\newpage
